### 2022-06-29 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@b77c93793d62675209a0550d7411ad7373fd06f4 🚀

Both of these regions are priority areas for sampling, especially given
predictions that they contain many bat hosts of undiscovered
betacoronaviruses.\textsuperscript{19,20} However, both the evolutionary
and ecological aspects of emergence risk are higher in southeast
Asia---a fact that will only become more relevant, as bats track
shifting climates and exchange viruses with other species, creating a
hotspot of elevated cross-species transmission unique to the
region.\textsuperscript{28,47} Bats---and the spillover of their
viruses---are also sensitive to anthropogenic factors others than
climate change, including deforestation and other kinds of habitat loss,
increased stress, and greater contact with potential bridge hosts like
domesticated species.\textsuperscript{26,48,49} This represents a
challenge for both conservation strategies and pandemic
prevention,\textsuperscript{50} but identifying areas at risk, and
protecting the health of bats and ecosystems within those zones, can be
a win-win intervention for both (add cites for DOIs:
10.1038/s41893-020-00640-z; 10.1016/S2542-5196(21)00031-0).

>>>>

Both of these regions are priority areas for sampling, especially given
predictions that they contain many bat hosts of undiscovered
betacoronaviruses.\textsuperscript{19,20} However, both the evolutionary
and ecological aspects of emergence risk are higher in southeast
Asia---a fact that will only become more relevant, as bats track
shifting climates and exchange viruses with other species, creating a
hotspot of elevated cross-species transmission unique to the
region.\textsuperscript{28,47} Bats---and the spillover of their
viruses---are also sensitive to anthropogenic factors others than
climate change, including deforestation and other kinds of habitat loss,
increased stress, and greater contact with potential bridge hosts like
domesticated species\textsuperscript{26,48,49} (add cite for
10.1038/nature13139). This represents a challenge for both conservation
strategies and pandemic prevention,\textsuperscript{50} but identifying
areas at risk, and protecting the health of bats and ecosystems within
those zones, can be a win-win intervention for both (add cites for DOIs:
10.1038/s41893-020-00640-z; 10.1016/S2542-5196(21)00031-0).
